Data Exploration: IUCN and AquaMaps

### 2015-09-10 data_explore.Rmd

p1 <- reg + geom_text(x = 50, y = 80000000, label = lm_eqn(spp_list), parse = TRUE)

>>>>

p1 <- reg + geom_text(x = 40, y = 300000000, label = lm_eqn(spp_list), parse = TRUE)

print(p1)
```
***

Looking at how many and what type (threat category) of species we are losing by setting a threshold of 0.4 on the aquamaps species.

```{r, warning=F,message=F}

#source mapping aquamaps.R to read in all aquamaps raw data. This takes a while so rendering will take a while. 
source('mapping aquamaps.R')
